Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
add requirements

\subsection{Requirements}
% refer to presentation here
% TODO Vielleicht könnt ihr ganz am Anfang einen Überblick geben was das System erfüllen muss, wie das geschieht erklärt ihr dann in den  Unterkapiteln

>>>>

\subsection{Requirements}

First, we want to give an overview of the functional and non-functional requirements, that the system has to fulfill.

The systems purpose is to facilitate trusted communication and collaboration between untrusting partners.
For this, it has to be possible to send messages between partners.
To ensure security and trust in the system, both partners need a way to verify the authenticity of a message.
This means that the system has to keep track of users and permissions.
To keep this maintainable, we will need a user-to-role and role-to-permission mapping.
This mapping should be flexible, i.e. creatable and modifyable at runtime.
Of course it also has to be queryable, so that the communicating partners can use it to check the authenticity of messages.

In order to make this system feasible in a production environment, we also require it to be reusable, measurable and cheap.
This implies keeping the amount of contracts, memory consumption and message calls low.
Measurability is required for evaluation and monitoring.
Because all computation done by smart contracts requires a certain amount of gas (and thus money), we want to keep the cost of our implementation as low as possible.

% TODO Vielleicht könnt ihr ganz am Anfang einen Überblick geben was das System erfüllen muss, wie das geschieht erklärt ihr dann in den  Unterkapiteln
